### 2021-06-06 paper/model_validation.tex
Add figures to be combined. Fix some label issues.
Add missing figures/data, comment out missing figures, and clean up subcaption layout.

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
  \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Federal State}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal states.}
\label{fig:state_fit}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit2}
\end{figure}

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
  % \includegraphics[width=\textwidth]{../figures/results/figures/incidences_by_group/state/full_combined_baseline_new_known_case}
\caption{Simulated and Empirical Infections by Federal State}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal states.}
\label{fig:state_fit}
\end{figure}

### 2021-06-06 paper/report.tex
Remove request for N PCR tests.
Add missing figures/data, comment out missing figures, and clean up subcaption layout.

        \textcolor{red}{Number of PCR tests}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/full_decomposition}

        \caption{
            Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}.

            The decomposition is based on Shapley values where the individual
            contribution of an intervention is its average contribution over different
            sizes of coalitions (combinations with other interventions). The individual
            contribution to a coalition is the difference between the effect size of the
            coalition with the particular intervention and without.
        }
        \label{fig:decompisition total cases}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

>>>>

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/full_decomposition}
        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}. The decomposition is based on Shapley values where the individual contribution of an intervention is its average contribution over different sizes of coalitions (combinations with other interventions). The individual contribution to a coalition is the difference between the effect size of the coalition with the particular intervention and without.}
        \label{fig:decompisition total cases}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
